Paper Title*

### 2018-12-27 paper.tex
propagation

The link budget of a wireless system or network is a measure of all the gains and losses from the
transmitter, through the propagation channel, to the target receiver. These gains and losses include
system gains and losses associated with the antenna, matching networks, etc. as well as losses
associated propagation channel itself (either though modelling or measured data).
Typically randomly varying channel mechanisms such as multipath and Doppler fading are taken into
account by factoring additional margin depending on the anticipated severity.
The link budget of a network wireless link can be expressed as:

\begin{equation} \label{eq:rx_sensitivity}
P^{dBm}_{RX} = P^{dBm}_{TX} + G^{dB}_{SYS} - L^{dB}_{SYS} - L^{dB}_{PATH}
\end{equation}

Where, $P^{dBm}_{RX}$ is the expected receive power at the receiver. $P^{dBm}_{TX}$ is the transmit power. $G^{dB}_{SYS}$ is the system gains such as transmitter and receiver antenna gain. $L^{dB}_{SYS}$ is the system losses such as transmitter and receiver line, circuit, antenna losses. $L^{dB}_{PATH}$ is the propagation path loss between transmitter and receiver antennas.

>>>>

The link budget of a wireless system or network is a measure of all the gains and losses from the transmitter, through the propagation channel, to the target receiver. Link budget of a wireless link can be calculated as:

\begin{equation} \label{eq:expected_rx_power}
P^{dBm}_{RX} = P^{dBm}_{TX} + G^{dB}_{SYS} - L^{dB}_{SYS} - L^{dB}_{PATH}
\end{equation}

\par Where, $P^{dBm}_{RX}$ is the expected receive power at the receiver. $P^{dBm}_{TX}$ is the transmit power. $G^{dB}_{SYS}$ is the system gains such as transmitter and receiver antenna gains. $L^{dB}_{SYS}$ is the system losses such as transmitter and receiver line, circuit, antenna losses. $L^{dB}_{PATH}$ is the propagation path loss between transmitter and receiver antennas.

\par Propagation loss can be calculated as:

\begin{equation} \label{eq:propagation_loss}
\begin{split}
P^{dB}_{PATH} = 40(1 - 4 \times 10^{-3} \times h){\log_{10} R|_{km}} \\
- 18 {\log_{10} h|_{m}} + 21 {\log_{10} f|_{MHz}} + 80
\end{split}
\end{equation}

\par Where $h$ is the gateway altitude and $f$ is the frequency of the signal. We assume that $h$ = 15 m and $f$ = 868 MHz, Propagation loss can be calculated as:

\begin{equation} \label{eq:propagation_loss}
P^{dB}_{PATH} = 120.5 + 37.6 {\log_{10} R|_{km}}
\end{equation}
